\ttitle

### 2015-06-13 Chapters/CPET_Survival.tex
Some minor changes before starting work today

\chapter{An investigation into the relationship between cardiopulmonary exercise testing, comorbidity, systemic inflammation and survival after pancreaticoduodenectomy for cancer.}
\label{ch_survival}

@@

Comorbidity is not only associated with postoperative morbidity and mortality (Section \ref{sec:comorbidity_risk_stratification}) but has also been reported to be associated with poor long-term survival in patients undergoing surgery several different cancers including colorectal cancer \parencite{} and breast cancer.\parencite{} With 10-year survival rates approaching 60\% and 80\% in these patients, it is not surprising that some patients with significant comorbidity may die from their comorbid disease rather than from cancer recurrence. However, cancer-specific survival is also shorter in patients with significant comorbidities.

>>>>

\chapter{An investigation into the relationship between cardiopulmonary exercise testing, comorbidity, systemic inflammation and survival after pancreaticoduodenectomy for pancreatic ductal adenocarcinoma.}
\label{ch_survival}

@@

Comorbidity is not only associated with postoperative morbidity and mortality (Section \ref{sec:comorbidity_risk_stratification}) but has also been reported to be associated with poor long-term survival in patients undergoing surgery for several different cancers including colorectal cancer \parencite{} and breast cancer.\parencite{} With 10-year survival rates approaching 60\% and 80\% respectively in patients with these cancers, it is not surprising that some patients with significant comorbidity die of their comorbid disease rather than from cancer recurrence. However, reports suggest that cancer-specific survival is also shorter in patients with significant comorbidities.
